### 2016-09-30 R/ITHIM.Rmd
Created road fatalaties figure from BikePedDeaths_09-13.csv

# Appendix

>>>>

```{r roadInjuries, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
roadFatalaties <- read.csv(file = "./../data/BikePedDeaths_09-13.csv", na.strings = c("998","999"))
roadFatalaties <- within(roadFatalaties, {
  ageClass <- convertToAgeClass(AGE)
  SEX <- ifelse(SEX == 1, "M", ifelse(SEX == 2, "F", NA))
  SEX <- factor(SEX, levels = c("F","M"))
})
roadFatalaties <- subset(roadFatalaties, !is.na(SEX))

p <- ggplot(roadFatalaties, aes(ageClass, fill = SEX))
p + geom_bar(position = "dodge") + theme_bw()+ theme(axis.text.x  = element_text(angle=90, vjust=0.5)) + scale_x_discrete(name="", labels = c("0-4","5-14","15-29","30-44","45-59","60-69","70-79","80+")) + facet_grid( death ~ ., scales = "free_y")
```
# Appendix
